### 2020-12-09 Thesis-Chapter4-Tools.tex
Create DFD key

The new syntax illustrates the data in more detail as it is stored, transferred, and operated on. By illustrating the
data itself, it eliminates the need for labels on lines and can be used to communicate entire protocols in a single
% diagram. \myfig{fig-dfd-key} contains the full set of symbols. In \mychap{chap-threatmodel} I create \acp{DFD} in this
style to analyze the threats already present and those that \ac{EA} would introduce.

% \begin{figure}[p]
%     \centering\CaptionFontSize
%     \includegraphics[width=\linewidth]{dfds/build/dfd-key.png}
%     \caption{A Diffie-Hellman key exchange illustrated with additional syntax}
%     \label{fig-dfd-key}
% \end{figure}

>>>>

The new syntax illustrates the data in more detail as it is stored, transferred, and operated on. By illustrating the
data itself, it eliminates the need for labels on lines and can be used to communicate entire protocols in a single
diagram. \myfig{fig-dfd-key} contains the full set of symbols. In \mychap{chap-threatmodel} I create \acp{DFD} in this
style to analyze the threats already present and those that \ac{EA} would introduce.

\begin{figure}[p]
    \centering\CaptionFontSize
    \includegraphics[width=0.85\linewidth]{dfds/build/dfd-key.png}
    \caption{Expanded set of DFD symbols}
    \label{fig-dfd-key}
\end{figure}
